---
title: "Data"
author: "Nina"
date: "05/05/2022"
output: html_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}}
source(here::here("Scripts/SetUp.R"))
```

## Data Understanding and Preparation 

In this first part, we will first download the data into R. Then, we will apply the necessary transformations on these data so that they can be correctly exploited for the following analysis. 

The database *bands3* is initially composed of 540 observation and 40 variables.


```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Loading data into R
bands3 <- read.csv2(here::here("Data/bands3.csv"))
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Response attribute transformation 
bands3$job_number <- as.character(bands3$job_number)
bands3$press <- as.character(bands3$press)
bands3$unit_number <- as.character(bands3$unit_number)
bands3$proof_cut <- as.numeric(bands3$proof_cut)
bands3$viscosity <- as.numeric(bands3$viscosity)
bands3$caliper <- as.numeric(bands3$caliper)
bands3$ink_temperature <- as.numeric(bands3$ink_temperature)
bands3$humidity <- as.numeric(bands3$humidity)
bands3$roughness <- as.numeric(bands3$roughness)
bands3$blade_pressure <- as.numeric(bands3$blade_pressure)
bands3$varnish_pct <- as.numeric(bands3$varnish_pct)
bands3$press_speed <- as.numeric(bands3$press_speed)
bands3$ink_pct <- as.numeric(bands3$ink_pct)
bands3$solvent_pct <- as.numeric(bands3$solvent_pct)
bands3$ESA_voltage <- as.numeric(bands3$ESA_voltage)
bands3$ESA_amperage <- as.numeric(bands3$ESA_amperage)
bands3$wax <- as.numeric(bands3$wax)
bands3$hardener <- as.numeric(bands3$hardener)
bands3$roller_durometer <- as.numeric(bands3$roller_durometer)
bands3$current_density <- as.numeric(bands3$current_density)
bands3$anode_space_ratio <- as.numeric(bands3$anode_space_ratio)
bands3$chrome_content <- as.numeric(bands3$chrome_content)
```

 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Database reduction 
index<- c(5,7,10,11,13:16,18:31,34:40)
bands3_reduced <- bands3%>%
  select(index)
```

After reading and understanding these variables, we realized that some of them were not necessary because they were not complete or/and did not bring any explanatory surplus to the analysis. We therefore decided to create a new database without these variables.

The new database *bands3_reduced* is now composed of 540 observations and 29 variables.

__Variables removed:__

- date
- cylinder_no
- customer
- job_number
- ink_color
- blade_mfg
- direct_steam
- unit_number
- ESA_voltage
- ESA_amperage
- anode_space_ratio

Here is an overview of the variables we have kept:
```{r, echo = FALSE}
str(bands3_reduced) 
```

We noticed some question marks (?) for some observations. We decided to replace them all with missing values (NA).

```{r, echo = FALSE}
bands3_reduced[bands3_reduced == "?"] <- NA
bands3_reduced[, 1:11] <- lapply(bands3_reduced[, 1:11], toupper)
```

