---
title: "DA_Project"
author: "Nina"
date: "4/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### EDA

Download useful R packages
```{r}
library(DT)
library(Hmisc)  
library(tidyverse)
library(tidyquant)
library(ggthemes)
library(RColorBrewer)
library(corrplot)
library(psych)
library(GGally)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(kableExtra)
library(DataExplorer)
library(inspectdf)
```

## 1. Data preparation
# 1.1 Loading data into R
 
```{r }
bands3 <- read.csv2("bands3.csv")
```

# 1.2 Response attribute transformation
 
```{r }
n <- dim(bands3)[1]
p <- dim(bands3)[2]
```
n = ROW = 540 observartions 
p = COLUMN = 40 variables/characteristics

## 2. Data structure and summary
 
```{r }
str(bands3)
head(bands3)
summary(bands3)
describe(bands3)
as_tibble(bands3)
datatable(bands3)
```

# 2.1 DataExpolrer library

```{r }
introduce(bands3[,-39])
plot_intro(bands3[,-39])
```

# a. Missing observations
```{r }
nrows <- nrow(bands3)
n.missing <- rowSums(is.na(bands3))
sum(n.missing > 0)/nrows
```
[1] 0
```{r }
n.complete <- sum(complete.cases(bands3))
n.complete/nrows
```
[1] 1
```{r }
plot_missing(bands3[,-39])
```

# b. Histograms
```{r }
plot_histogram(bands3[,-39])
```

# c. Density plots
```{r }
plot_density(bands3[,-39],
             ggtheme = theme_bw())
```

# d. Side-by-side boxplots
???

# e. Variables summaries 
???
```{r }
quanti<-1:40
mat<-matrix(0, length(quanti), 7)
colnames(mat)<-c("Min.", "1st Qu.", "Median", "Mean", "Sd", "3rd Qu.", "Max.")
rownames(mat)<-names(bands3)[quanti]
mat[,1]<-apply(bands3[,quanti], 2, min)
mat[,2]<-apply(bands3[,quanti], 2, quantile, 0.25)
mat[,3]<-apply(bands3[,quanti], 2, median)
mat[,4]<-apply(bands3[,quanti], 2, mean)
mat[,5]<-apply(bands3[,quanti], 2, sd)
mat[,6]<-apply(bands3[,quanti], 2, quantile, 0.75)
mat[,7]<-apply(bands3[,quanti], 2, max)
print(round(mat, 2))
```

# f. Pairwise comparison
```{r }
bands3.quant <- bands3[,quanti]
plot_correlation(bands3.quant, type = 'c', cor_args = list('use'='complete.obs'))
pairs(bands3.quant)
```
???
```{r }
pairs.panels(bands3.quant)
ggpairs(bands3)
```
???
```{r }
ggpairs(bands3[,-39], ggplot2::aes())
```
???
```{r }
cor(bands3.quant)
```
???
```{r }
corrplot(cor(bands3.quant))
```
???
```{r }
d<-correlate(bands3.quant)         
d %>%
+   shave() %>% # Remove the upper triangle
+   fashion()
```
???
```{r }
d %>% network_plot(min_cor=.1)
```
???
```{r }
corrplot.mixed(cor(bands3.quant), order="hclust", tl.col="black")
```
???
```{r }
ggcorrplot(cor(bands3.quant), p.mat=cor_pmat(bands3[,quanti]), hc.order=TRUE, type='lower')
```
???

## 2.2 Inspected library

```{r }
x<-inspect_types(bands3[,-39])
show_plot(x, col_palette=2)

x<-inspect_na(bands3[,-39])
show_plot(x, col_palette=5)

x<-inspect_num(bands3[,-39])
show_plot(x, col_palette=3)

x<-inspect_cat(bands3[,-39]) 
show_plot(x)

x<-inspect_cor(bands3[,-39])
show_plot(x, col_palette=4)
```

## 2.3 Outliers
 



```{r }

```
